On the Bit Complexity of Finding Points in Connected Components of a Smooth Real Hypersurface

### 2020-02-02 main.tex
Updated Section 6

Since $\deg \Phi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $D^n,$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then $0$ is a regular value of $\Phi_{A}$, which means that 

@@

\jac_\textit{\textbf{x}} \Phi_A 

>>>>

Since $\deg \Psi \leq D,$ it follows by Theorem 5.1 that a hypersurface $\Delta_1 \subset \C^{n^2}$ exists, of degree at most $D^n,$ with the property that, if $A \in \C^{n^2}-\Delta_1,$ then $0$ is a regular value of $\Psi_{A}$, which means that 

@@

\jac_\textit{\textbf{x}} \Psi_A 
